\section{Examples of Markdown Syntax}

The examples given in the ProfHacker blog post were all indented to keep
them as code rather than have Markdown translate them to HTML. Here the
examples in this plain text file will be translated to various file
formats, also available in this repository.

\subsection{The Examples}

\subsubsection{Italics}

Be sure to read William James, \emph{The Varieties of Religious
Experience}.

\subsubsection{Bold}

James's book will \textbf{definitely} be covered on the final exam.

\subsubsection{Block quotes}

You must be able to discuss James's definition of religion:

\begin{quote}
Religion, therefore, as I now ask you arbitrarily to take it, shall mean
for us the feelings, acts, and experiences of individual men in their
solitude, so far as they apprehend themselves to stand in relation to
whatever they may consider the divine.

\end{quote}
\subsubsection{A link}

James's book is available in full text at Google Books
\url{http://books.google.com/books?id=OESbXvtUkIsC}.

\subsubsection{Numbered and unnumbered lists}

\begin{itemize}
\item
  An item.
\item
  Another item.
\item
  Yet another item.
\item
  Item one.
\item
  Item two.
\item
  Item three.
\end{itemize}
\subsubsection{A Footnote}

William James offered a narrow definition of religion for the purposes
of the Gifford Lectures.\footnote{William James, \emph{The Varieties of
  Religious Experience} (New York: Longman, Green, and Co., 1903); cf.
  Thomas Tweed, \emph{Crossing and Dwelling: A Theory of Religion}
  (Cambridge, MA: Harvard University Press, 2008).}
